A Comparison of Dimensionality Reduction Techniques for Robotic Motion Planning

### 2016-05-11 paper/paper.tex
added to paper

We used FeatureAgglomeration, TruncatedSVD, PCA, KernelPCA, RandomizedPCA, and
our own "Trained Johnson-Lindestrauss" to perform dimensionality reduction.

PCA: Principle Component Analysis, or PCA, transforms a set of variables in
their "principle components", or linearly uncorrelated variables.\

>>>>

We used Feature Agglomeration, Truncated SVD, PCA, Kernel PCA, Randomized PCA, and
our own "Trained Johnson-Lindestrauss" to perform dimensionality reduction. We will briefly summarize each of these techniques.

PCA: Principle Component Analysis, or PCA, transforms a set of variables into 
their "principle components", or linearly uncorrelated variables. In other words, the axes of the dataset in question are reoriented so the Rayleigh quotient, which is related to the covariance of the dataset, along the first axis is maximized. After the first axis has been set, the second axis is then set to maximize the Rayleigh quotient of the dataset along that axis, and so on, so that the first axis has the highest Rayleigh quotient, the second axis has the second highest, and so on. Dimensionality reduction is then performed by chopping off the axes with the lowest Rayleigh quotients (which corresponded to axes with the lowest variance). \

Kernel PCA: Kernel PCA enables non-linear dimensionality reduction by using kernels to create a non-linear mapping from a high dimension to a lower dimension.

Randomized PCA: In Randomized PCA, computations are sped up by only approximating the singular vectors of the components.

Feature Agglomeration: Feature Agglomeration groups together similar features to reduce the number of features. It does this by using agglomerative clustering, in which every data point starts as a cluster, and clusters are merged together.

Truncated SVD:
